### 2016-05-04 paper/main.tex
update

From these ``local" measures of significance, we can also compute average error rates over subsets of observations
$\Gamma \subset \{1,\dots,J\}$. For example, 
\begin{equation} \label{eqn:FSRhat}
\widehat\FSR(\Gamma):= (1/|\Gamma|) \sum_{j \in \Gamma} \lfsr_j 
\end{equation}
is an estimate of the total proportion of errors made if we were to estimate the sign of all effects in $\Gamma$
(an error measure analogous to the usual (tail) FDR).
And, we can define the ``$s$-value" 
\begin{equation} \label{eqn:qvalue}
s_j := \widehat \FSR(\{k: \lfsr_k \leq \lfsr_j\}) 
\end{equation}
as a measure of significance analogous to Storey's $q$-value \cite{storey.03}.
(Replacing $\lfsr_j$ with $\lfdr_j$ in these definitions gives estimates for the usual $\FDR(\Gamma)$, and a $q$ value for each observation respectively.)

@@

We illustrate the effects of the UA, and the difference with existing methods, using a simple simulated dataset
 with the true effects $\beta_j \sim N(0,1)$ (so with $s_j=1$, $\bhat_j  \sim N(0,2)$). Note that none of the effects are truly null,
but nonetheless there are many $p$ values near 1 and $z$ scores near 0 (Figure \ref{fig:ZA}).  We used each of the methods
\qvalue, \locfdr, \mixfdr and \ashr to decompose the $z$ scores ($z_j = \bhat_j$), or their corresponding $p$ values, into null and alternative components.
(Here we are using the fact that these methods all provide an estimate of the \lfdr{} for each observation, which
implies such a decomposition;  specifically the average \lfdr{} within each histogram bin estimates the fraction of observations in that bin that come from the null vs the alternative component.) The results (Figure \ref{fig:ZA}) illustrate a clear difference between the existing methods and our method:
all the existing methods have a ``hole"  in the alternative $z$ score distribution near 0, whereas \ashr, due to the UA, has a mode near 0.
%Although \mixfdr does not formally make the \sZA, its decomposition
%exhibits a similar hole. 
%In contrast, due to the UA, the alternative $z$ score distribution for \ashr is required to have a mode at 0, 
%effectively ``filling in" the hole.  
(Of course the null distribution also has a peak at 0, and the local fdr 
 under the UA is still smallest for $z$ scores that are far from zero -- i.e. large $z$ scores remain the ``most significant".)

@@

I thank J.~Lafferty for pointing out the convexity of the likelihood function, which lead to our improved implementation with interior point methods. 
Statistical analyses were conducted in the {\sf R} programming language \cite{Rcore:2012}, Figures produced using the {\tt ggplot2} package \cite{ggplot2}, and text
prepared using \LaTeX. Development of the methods in this paper was greatly enhanced by the use of the {\tt knitr} package \cite{xie2013dynamic}  within the RStudio GUI, and 
git and github. The {\tt ashr} R package is available from \href{http://github.com/stephens999/ashr}{http://github.com/stephens999/ashr} and includes contributions 
from Chaoxing (Rick) Dai, Mengyin Lu, and Tian Sen.

>>>>

From these ``local" measures of significance, we can also compute average error rates over subsets of observations
$\Gamma \subset \{1,\dots,J\}$. For example, 
\begin{equation} \label{eqn:FSRhat}
\widehat\FSR(\Gamma):= (1/|\Gamma|) \sum_{j \in \Gamma} \lfsr_j 
\end{equation}
is an estimate of the total proportion of errors made if we were to estimate the sign of all effects in $\Gamma$
(an error measure analogous to the usual (tail) FDR).
And, we can define the ``$s$-value" 
\begin{equation} \label{eqn:qvalue}
s_j := \widehat \FSR(\{k: \lfsr_k \leq \lfsr_j\}) 
\end{equation}
as a measure of significance analogous to Storey's $q$-value \cite{storey.03}.
(Replacing $\lfsr_j$ with $\lfdr_j$ in these definitions gives an estimate for the usual $\FDR(\Gamma)$, and an estimated $q$ value for each observation respectively.)

@@

We illustrate the effects of the UA, and the difference with existing methods, using a simple simulated dataset
 with the true effects $\beta_j \sim N(0,1)$ (so with $s_j=1$, $\bhat_j  \sim N(0,2)$). Note that none of the effects are truly null,
but nonetheless there are many $p$ values near 1 and $z$ scores near 0 (Figure \ref{fig:ZA}).  We used each of the methods
\qvalue, \locfdr, \mixfdr and \ashr to decompose the $z$ scores ($z_j = \bhat_j$), or their corresponding $p$ values, into null and alternative components.
Here we are using the fact that these methods all provide an estimate of the \lfdr{} for each observation, which
implies such a decomposition;  specifically the average \lfdr{} within each histogram bin estimates the fraction of observations in that bin that come from the null vs the alternative component. The results (Figure \ref{fig:ZA}) illustrate a clear difference between the existing methods and our method:
all the existing methods have a ``hole"  in the alternative $z$ score distribution near 0, whereas \ashr, due to the UA, has a mode near 0.
%Although \mixfdr does not formally make the \sZA, its decomposition
%exhibits a similar hole. 
%In contrast, due to the UA, the alternative $z$ score distribution for \ashr is required to have a mode at 0, 
%effectively ``filling in" the hole.  
(Of course the null distribution also has a peak at 0, and the local fdr 
 under the UA is still smallest for $z$ scores that are far from zero -- i.e. large $z$ scores remain the ``most significant".)

@@

I thank J.~Lafferty for pointing out the convexity of the likelihood function, which lead to an improved implementation with interior point methods. 
Statistical analyses were conducted in the {\sf R} programming language \cite{Rcore:2012}, Figures produced using the {\tt ggplot2} package \cite{ggplot2}, and text
prepared using \LaTeX. Development of the methods in this paper was greatly enhanced by the use of the {\tt knitr} package \cite{xie2013dynamic}  within the RStudio GUI, and 
git and github. The {\tt ashr} R package is available from \href{http://github.com/stephens999/ashr}{http://github.com/stephens999/ashr} and includes contributions 
from Chaoxing (Rick) Dai, Mengyin Lu, and Tian Sen.
